### 2012-03-15 docs/architecture/architecture.tex
add ref for BCs

A \bctower\ holds the information about what boundary conditions are
in effect for each variable in a \maestro\ simulation.  \MarginPar{better description?}

@@

@@

{\tt ell\_bc\_level\_array} is the analog to {\tt
  adv\_bc\_level\_array} for the elliptic solves in \maestro.  This
will come into play in the multigrid portions of the code.  The
actions that are used for {\tt ell\_bc\_level\_array} are either
Dirichlet or Neumann boundary condtions.  For the velocity
projections, we are dealing with a pressure-like quantity, $\phi$, so
the pressure boundary conditions here reflect the behavior we want for
the velocity.  You want $d\phi/dn=0$ in places where the incoming
velocity to the elliptic solve must match the velocity you want after
the projection (e.g.\ inflow, solid walls).  For outlet boundaries,
setting $\phi = 0$ allows the velocity to adjust as needed to the
domain. \MarginPar{reference here would be nice}

>>>>

A \bctower\ holds the information about what boundary conditions are
in effect for each variable in a
\maestro\ simulation.  These are interpretted by the ghost cell filling 
routines.  See \S~\ref{sec:arch:bcs} for more detail.

@@

\label{sec:arch:bcs}

@@

{\tt ell\_bc\_level\_array} is the analog to {\tt
  adv\_bc\_level\_array} for the elliptic solves in \maestro.  This
will come into play in the multigrid portions of the code.  The
actions that are used for {\tt ell\_bc\_level\_array} are either
Dirichlet or Neumann boundary condtions.  For the velocity
projections, we are dealing with a pressure-like quantity, $\phi$, so
the pressure boundary conditions here reflect the behavior we want for
the velocity.  You want $d\phi/dn=0$ in places where the incoming
velocity to the elliptic solve must match the velocity you want after
the projection (e.g.\ inflow, solid walls).  For outlet boundaries,
setting $\phi = 0$ allows the velocity to adjust as needed to the
domain (see, for example, \cite{almgrenBellSzymczak:1996}).
